msb106_assignment

### 2024-01-17 msb106_assignment.qmd
mk

```{r}
data <- data %>% 
  mutate(deg_urb = case_when(
    deg_urb == "DEG1" ~ "Cities",
    deg_urb == "DEG2" ~ "Towns/Suburbs",
    deg_urb == "DEG3" ~ "Rural areas",
    TRUE ~ deg_urb  # Hvis ingen av de over er oppfylt, behold eksisterende verdi
  ))
```

@@

>>>>

```{r}
data <- data %>% 
  mutate(deg_urb = case_when(
    deg_urb == "DEG1" ~ "Cities",
    deg_urb == "DEG2" ~ "Towns/Suburbs",
    deg_urb == "DEG3" ~ "Rural areas"
  ))
```

@@

```{r}
# Installer ggplot2 hvis du ikke har det installert
install.packages("ggplot2")

# Last inn ggplot2-pakken
library(ggplot2)
```

```{r}
# Assuming you have a column named "population_growth" and "country" in your dataset

# Filter data for "Cities" and create a plot with lines for each country
cities_plot <- data |> 
  filter(deg_urb == "Cities") |> 
  ggplot(aes(x = TIME_PERIOD, y = OBS_VALUE, color = geo)) +
  geom_line() +
  labs(title = "Population Growth Trends in Cities by Country",
       x = "Year",
       y = "Population Growth",
       color = "Country")

# Display the plot for "Cities"
print(cities_plot)

```
